Abstractions for Multi-Sorted Substitutions

### 2024-03-11 paper/paper.tex
Update.

  For this purpose, the \ACode{\ACon{CKit}} abstraction, needs
  to satisfy two requirements:
  it needs to provide us with enough machinery to define composition, but
  it also needs to provide us with enough axioms that we are able to instantiate
  the \ACode{\ACon{CTraversal}}. It is defined as followed:
  \LibCode\KCKit
  The \ACode{\AField{\_\&/⋯\_}} operation takes a variable or term
  (according to \ACode{K₁}) and a renaming or substitution
  (according to \ACode{K₂}) and performs the map traversal returning
  a variable or term (according to \ACode{K₁⊔K₂}).
  The third parameter \ACode{K₁⊔K₂} can be seen as a functional
  dependency and is completely determined by the choice of \ACode{K₁}
  and \ACode{K₂}.

>>>>

  For this purpose, the \ACode{\ACon{CKit}} abstraction, needs
  to satisfy two requirements:
  it needs to provide us with enough machinery to define composition, but
  it also needs to provide us with enough axioms that we are able to instantiate
  the \ACode{\ACon{CTraversal}}. It is defined as followed:
  \LibCode\KCKit
  The \ACode{\AField{\_\&/⋯\_}} operation takes a variable or term
  (according to \ACode{K₁}) and a renaming or substitution
  (according to \ACode{K₂}) and performs the map traversal returning
  a variable or term (according to \ACode{K₁⊔K₂}).
  The third parameter \ACode{K₁⊔K₂} can be seen as a functional
  dependency\cite{DBLP:conf/esop/Jones00} and is completely determined
  by the choice of \ACode{K₁} and \ACode{K₂}.
